---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# term

<!-- badges: start -->
[![Lifecycle: maturing](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
[![Travis build status](https://travis-ci.com/poissonconsulting/term.svg?branch=master)](https://travis-ci.com/poissonconsulting/term)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/poissonconsulting/term?branch=master&svg=true)](https://ci.appveyor.com/project/poissonconsulting/term)
[![Codecov test coverage](https://codecov.io/gh/poissonconsulting/term/branch/master/graph/badge.svg)](https://codecov.io/gh/poissonconsulting/term?branch=master)
[![License: MIT](https://img.shields.io/badge/License-MIT-green.svg)](https://opensource.org/licenses/MIT)
[![Tinyverse status](https://tinyverse.netlify.com/badge/term)](https://CRAN.R-project.org/package=term)
[![CRAN status](https://www.r-pkg.org/badges/version/term)](https://cran.r-project.org/package=term)
![CRAN downloads](http://cranlogs.r-pkg.org/badges/term)
<!-- badges: end -->

`term` is an R package to create, manipulate and query S3 vectors of parameter terms 
such as 'alpha', 'beta[3]' and 'sigma2[1,4]'.

## Installation 

To install the latest release version from [CRAN](https://cran.r-project.org)
```
install.packages("term")
```

To install the latest development version from [GitHub](https://github.com/poissonconsulting/term)
```
# install.packages("remotes")
remotes::install_github("poissonconsulting/term")
```

## Demonstration

```{r}
library(term)

# a term vector can be created from a character vector
term <- as.term(c("sigma", "beta[2,2]", "alpha[1]", "alpha[2]", "beta[1,1]", 
                  "beta[2,1]", "beta[1,2]"))

print(term)

# term vectors can be sorted (by the term parameter names and indices)
term <- sort(term)
print(term)

# and the parameters extracted
parameters(term)

# as well as the dimensions of each parameter
pdims(term)

# and the index of each term
tindex(term)
```

## Contribution

Please report any [issues](https://github.com/poissonconsulting/term/issues).

[Pull requests](https://github.com/poissonconsulting/term/pulls) are always welcome.

Please note that the 'term' project is released with a [Contributor Code of Conduct](https://poissonconsulting.github.io/term/CODE_OF_CONDUCT.html).
By contributing to this project, you agree to abide by its terms.
