---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# term

<!-- badges: start -->
[![Lifecycle: maturing](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
[![Travis build status](https://travis-ci.com/poissonconsulting/term.svg?branch=master)](https://travis-ci.com/poissonconsulting/term)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/poissonconsulting/term?branch=master&svg=true)](https://ci.appveyor.com/project/poissonconsulting/term)
[![Codecov test coverage](https://codecov.io/gh/poissonconsulting/term/branch/master/graph/badge.svg)](https://codecov.io/gh/poissonconsulting/term?branch=master)
[![License: MIT](https://img.shields.io/badge/License-MIT-green.svg)](https://opensource.org/licenses/MIT)
[![Tinyverse status](https://tinyverse.netlify.com/badge/term)](https://CRAN.R-project.org/package=term)
[![CRAN status](https://www.r-pkg.org/badges/version/term)](https://cran.r-project.org/package=term)
![CRAN downloads](http://cranlogs.r-pkg.org/badges/term)
<!-- badges: end -->

`term` is an R package to create, manipulate, query and repair vectors of parameter terms.
Parameter terms are the labels used to reference values in vectors, matrices and arrays.
They represent the names in coefficient tables and the column names in 
`mcmc` and `mcmc.list` objects.

## Installation 

To install the latest release from [CRAN](https://cran.r-project.org)
```{r, eval=FALSE}
install.packages("term")
```

To install the developmental version from [GitHub](https://github.com/poissonconsulting/term)
```{r, eval=FALSE}
# install.packages("remotes")
remotes::install_github("poissonconsulting/term")
```

To install the latest developmental release from the Poisson drat [repository](https://github.com/poissonconsulting/drat)
```{r, eval=FALSE}
# install.packages("drat")
drat::addRepo("poissonconsulting")
install.packages("term")
```

## Demonstration

### Creating Term Vectors
```{r}
library(term)

# character vectors can be converted into term vectors
term <- as.term(c(
  "alpha[1]", "alpha[2]", "beta[1,1]", "beta[2,1]",
  "beta[1,2]", "beta[2,2]", "sigma"
))

# term vectors print like character vectors
term

# they are S3 class objects that also inherit from character
str(term)

# term vectors can also be created from numeric atomic objects
as.term(matrix(1:4, 2), "theta")
```

### Querying Term Vectors
```{r}
# get the parameter names
pars(term)
# and parameter dimensions
pdims(term)

# get the parameter names by term
pars(term, terms = TRUE)
# and the term indices
tindex(term)
```

### Validating Term Vectors
```{r}
# term vectors can be tested for whether they have (parseably) valid,
# (dimensionally) consistent and complete terms.

# valid terms
valid_term(as.term(c("a", "a[1]", "a [2]", " b [3  ] ", "c[1,10]")))

# invalid terms
valid_term(as.term(c("a a", "a[]", "a[2", " b[3 3]", "c[1,10]c")))

# consistent terms
consistent_term(as.term(c("a", "a[2]", "b[1,1]", "b[10,99]")))

# inconsistent terms
consistent_term(as.term(c("a", "a[2,1]", "b[1,1]", "b[10,99,1]")))

# complete terms
is.incomplete_terms(as.term(c("a", "a[2]", "b[1,1]", "b[2,1]")))

# incomplete terms
is.incomplete_terms(as.term(c("a", "a[3]", "b[1,1]", "b[2,2]")))
```

### Checking Term Vectors
```{r, error=TRUE}
x <- as.term(c("a[1]", "a[3]"))
chk_term(x, validate = "valid")
chk_term(x, validate = "complete")
```

### Repairing Term Vectors
```{r}
term <- as.term(c("b[4]", "b   [2]", "b", "b[1", "b[2, 2]", "b", "a [ 1 ] ", NA))
term

# valid terms can be repaired (invalid terms are converted to missing values)
term <- repair_terms(term)
term

# missing values can easily removed
term <- term[!is.na(term)]
term

# and only unique values retained
term <- unique(term)
term

# a term vector can be sorted by parameter name and index
term <- sort(term)
term

# an inconsistent term removed
term <- term[term != "b[2,2]"]
term

# and incomplete terms completed
term <- sort(complete_terms(term))
term
```

## Contribution

Please report any [issues](https://github.com/poissonconsulting/term/issues).

[Pull requests](https://github.com/poissonconsulting/term/pulls) are always welcome.

Please note that the 'term' project is released with a [Contributor Code of Conduct](https://poissonconsulting.github.io/term/CODE_OF_CONDUCT.html).
By contributing to this project, you agree to abide by its terms.
